Global study of well-being and internet adoption | Online analysis supplement

### 2022-03-24 index.Rmd
Refactor

---
title: Global study of well-being and internet adoption | Online analysis supplement
description: |
  Online analysis supplement for "A global study of adolescents’ digital technology adoption and its associations with well-being and mental health" (Vuorre and Przybylski, in prep)
author: Matti Vuorre & Andy Przybylski
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::bs4_book
url: https://digital-wellbeing.github.io/global-wbmh
biblio-style: apalike
---

# Preface

This repository ([GitHub](https://github.com/digital-wellbeing/global-wbmh) / [OSF](https://osf.io/ys7m9/)) contains the code and synthetic datasets required to reproduce all analyses reported in our manuscript, *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, in preparation). These analyses are presented in the [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh).

## Materials

- [Preprint]()  
  - A publicly available version of our manuscript in advance of peer-review and formal publication
- [GitHub repository](https://github.com/digital-wellbeing/global-wbmh)  
  - A version controlled repository containing all the raw data and code in this project
- [OSF repository](https://osf.io/ys7m9/)  
  - An archived permanent copy of the GitHub repository
- [Online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)
  - The output document of our analyses

## Reproducibility

The code that we used to clean and analyse the data are organised in R Markdown (`.Rmd`) files in this directory, which are meant to be run in the sequence indicated by their numeric prefixes. To run all the cleaning and analyses, and compile the resulting document ([the online analysis supplement](https://digital-wellbeing.github.io/global-wbmh)), run `bookdown::render_book()` in R or click "Build Book" in the RStudio IDE.

### Docker

To ensure the reproducibility of our analyses, you can use Docker:

Build the Docker image
```
docker build \
    --build-arg R_VERSION=4.1.1 \
    --build-arg RENV_VERSION=0.14.0 \
    -t global-wbmh .
```

Run the container and render output
```
docker run \
    --rm \
    -v "$(pwd):/home/" \
    -v "/home/renv/library" \
    -e MAX_CORES=1 \
    global-wbmh \
    R -e 'renv::restore(prompt = FALSE); rmarkdown::render("index.Rmd")'
```

>>>>

# Preface {.unnumbered}

Welcome! This document is the online analysis supplement to *Global mental health and well-being in the internet age* (Vuorre & Przybylski, [preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

::: {.callout-note}
### How to reproduce our results

The analyses were conducted in R, and can be reproduced locally:

1. Clone the github repo
  - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
      OR
  - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2. Prepare the R environment
  - Terminal: `Rscript -e "renv::restore()"`  
      OR
  - RStudio: Click renv -> Restore Library in the Packages panel

3. Render the source files to a Quarto book
 - Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
  - Terminal: `quarto render`  
      OR
  - RStudio: Open the project (`global-wbmh.Rproj`) and click Render in the Build panel

::: {.callout-important}
The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
**The models take several hours/days each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason it might be easier to run the individual `.Rmd` files interactively in RStudio.
:::

If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
:::
